% Created 2013-01-31 Thu 12:14
\documentclass[12pt,bigger]{beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{soul}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{hyperref}
\tolerance=1000
\setbeamertemplate{frametitle}[default][center]
\mode<beamer>{\usetheme{Warsaw}}
\providecommand{\alert}[1]{\textbf{#1}}

\title{Mid Sem-1 progress review meeting}
\author{Deepti Aggarwal}
\date{[2013-02-01 Friday]}

\begin{document}

\maketitle




\section{Work accomplished in January}
\label{sec-1}
\begin{frame}
\frametitle{Renarration service for Alipi framework:}
\label{sec-1-1}

\begin{enumerate}
\item Plugin integration: Twitter integration is still left along with
   some more refinement of the plugin.
\item Worked on an initial draft of Alipi.
\item Improved thesis chapter on literature survey of web accessibility.
\end{enumerate}
\end{frame}
\begin{frame}
\frametitle{Power of Friends:}
\label{sec-1-2}

\begin{enumerate}
\item Paper submitted in CHI 2013.
\item Chapter done.
\end{enumerate}
\end{frame}
\begin{frame}
\frametitle{Thesis writing:}
\label{sec-1-3}

\begin{enumerate}
\item Worked on Introduction chapter of the thesis.
\item Added Appendix.
\end{enumerate}
\end{frame}
\section{Work to be accomplished by next month end}
\label{sec-2}
\begin{frame}
\frametitle{Alipi paper submission}
\label{sec-2-1}

\begin{enumerate}
\item Work on the paper draft.
\item Conduct user study in the R\&D showcase.
\end{enumerate}
\end{frame}
\begin{frame}
\frametitle{Thesis completion}
\label{sec-2-2}

Incomplete chapters: Introduction, Re-narration service to Alipi and
Conclusion.
\end{frame}
\section{Deadlines to follow}
\label{sec-3}

W4A 2013 (15th Feb.)

\end{document}
